\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex
BATE-V1

It can be rewritten as
\iffalse
\begin{equation}
\begin{cases}
R_{dk}^{\mathbf{z}} < 1- A_d^{\mathbf{z}}+M\times A_d^{\mathbf{z}},&{\forall d \in D, \mathbf{z} \in Z, k\in K.} \\
R_{dk}^{\mathbf{z}}>=A_d^{\mathbf{z}},&{\forall d \in D, \mathbf{z} \in Z, k\in K.} \\
A_d^{\mathbf{z}} \in\{0,1\},&{\forall d \in D, \mathbf{z} \in Z.} \\
\end{cases}
\label{A-z2}
\end{equation}
\fi
\begin{equation}
\label{A-z2}
\begin{array}{rll}
q_d^{\mathbf{z}} \in &\!\!\{0,1\} &{\forall d \in \hat{D}, \mathbf{z} \in Z} \\
R_{dk}^{\mathbf{z}} < &\!\! M\times q_d^{\mathbf{z}}+1-q_d^{\mathbf{z}} &{\forall d \in \hat{D},  k\in K} \\
R_{dk}^{\mathbf{z}} \ge &\!\!  q_d^{\mathbf{z}}, &{\forall d \in \hat{D},  k\in K}
\end{array}
\end{equation}
where $M$ is an constant larger than the upper bound of $R_{dk}^{\mathbf{z}}$.
%,\forall d \in D, k\in K,\mathbf{z} \in Z$.
%It is easily to  prove  (\ref{A-z2}) equals to  (\ref{CA}).
%Here, our consideration is tunnel $t$ might be unavailable (i.e., $v_t^{\mathbf{z}} =0$) under a network scenario, but if $R_{dk}^{\mathbf{z}} \ge 1$ holds, then this scenario is still \textit{qualified}, i.e., 
%$\mathbf{z} \propto <d, \{f_d^t\}> \quad \Leftrightarrow \quad \forall k, A_d^{\mathbf{z}}=1$.

@@

\begin{proof}
The all-or-nothing multi-commodity flow problem, which is known to be NP-hard\cite{inproceedings2}, 
can be regarded as a special case of our failure recovery problem (\ref{BATE-recovery}).
Consider an undirected graph $G = (V,E)$ and a set of $k$ source-destination pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
where each pair $s_it_i$ corresponds to a commodity flow to be sent from the source node $s_i$ to the destination node $t_i$ with demand $d_i$.
Let $\mathcal{P}_i$ denote the path set for pair $s_it_i$.
$L_{pe}$ denotes whether path $p$ goes through link $e$ and $f_{ip}$ is the allocation result of commodity $i$ over path $p$.
The  all-or-nothing multi-commodity flow problem tries to find a maximum weight routable set:
\begin{equation}
\begin{aligned} \label{P}
&maximize  \sum_{i=1}^k w_i \times y_i\\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t. &\forall e \in E: \sum_{i=1}^k\sum_{p\in \mathcal{P}_i}f_{ip}L_{pe} \le c_e \\
     &\forall  1\le i \le k  : y_i=
\begin{cases}
1 &\text{$\sum_{p \in \mathcal{P}_i}f_{ip} \ge d_i$}\\
0 &\text{$\sum_{p\in \mathcal{P}_i}f_{ip} < d_i$}
\end{cases}\\
\end{array}
\end{aligned}
\end{equation}
Where $y_i$ denotes whether commodity flow $i$ is routable.
Consider a special case of the failure recovery problem, where $\mu_d=0$ for every $d$.
This means, if the allocated bandwidth is no less than the demand, 
then the profit is 1, or the profit is 0 otherwise.
We transform the all-or-nothing multi-commodity flow problem to this case as follows:
\textbf{TBD:
We consider setting the admitted demand from tenants and their bandwidth target in 
the failure recovery as the multi-commodities and their bandwidth demand in the all-or-nothing multi-commodity flow problem.}
%If we can solve the special case of the admission control problem with a polynomial time algorithm, we would obtain the routable multi-commodity flow set  in the all-or-nothing multi-commodity flow problem.  
Therefore, the failure recovery problem is at least as hard as the all-or-nothing multi-commodity flow
problem, which is known to be NP-hard. This completes the proof.
%If we regard $j \in J$ as a multi-commodity flow pair and the topology as the undirected graph.
%$g_j$ denotes whether multi-commodity flow $j$ is able to be routed.
%Then WAPM-S problem can be seen as a variant of all-or-nothing multi-commodity flow problem and it is NP-hardness.
\end{proof}

>>>>

It can be rewritten as
\iffalse
\begin{equation}
\begin{cases}
R_{dk}^{\mathbf{z}} < 1- A_d^{\mathbf{z}}+M\times A_d^{\mathbf{z}},&{\forall d \in D, \mathbf{z} \in Z, k\in K.} \\
R_{dk}^{\mathbf{z}}>=A_d^{\mathbf{z}},&{\forall d \in D, \mathbf{z} \in Z, k\in K.} \\
A_d^{\mathbf{z}} \in\{0,1\},&{\forall d \in D, \mathbf{z} \in Z.} \\
\end{cases}
\label{A-z2}
\end{equation}
\fi
\begin{equation}
\label{A-z2}
\begin{array}{rll}
q_d^{\mathbf{z}} \in &\!\!\{0,1\}, &{\forall d \in \hat{D}, \mathbf{z} \in Z} \\
R_{dk}^{\mathbf{z}} < &\!\! M\times q_d^{\mathbf{z}}+1-q_d^{\mathbf{z}}, &{\forall d \in \hat{D},  k\in K} \\
R_{dk}^{\mathbf{z}} \ge &\!\!  q_d^{\mathbf{z}}, &{\forall d \in \hat{D},  k\in K}
\end{array}
\end{equation}
where $M$ is a constant larger than the upper bound of $R_{dk}^{\mathbf{z}}$.
%,\forall d \in D, k\in K,\mathbf{z} \in Z$.
%It is easily to  prove  (\ref{A-z2}) equals to  (\ref{CA}).
%Here, our consideration is tunnel $t$ might be unavailable (i.e., $v_t^{\mathbf{z}} =0$) under a network scenario, but if $R_{dk}^{\mathbf{z}} \ge 1$ holds, then this scenario is still \textit{qualified}, i.e., 
%$\mathbf{z} \propto <d, \{f_d^t\}> \quad \Leftrightarrow \quad \forall k, A_d^{\mathbf{z}}=1$.

@@

\begin{proof}
The all-or-nothing multi-commodity flow problem, which is known to be NP-hard\cite{inproceedings2}, 
can be regarded as a special case of our failure recovery problem (\ref{BATE-recovery}).
Consider an undirected graph $G = (V,E)$ and a set of $k$ source-destination pairs: $s_1t_1, s_2t_2,..., s_kt_k$,
where each pair $s_it_i$ corresponds to a commodity flow to be sent from the source node $s_i$ to the destination node $t_i$ with demand $d_i$.
Let $\mathcal{P}_i$ denote the path set for pair $s_it_i$.
$L_{pe}$ denotes whether path $p$ goes through link $e$ and $f_{ip}$ is the allocation result of commodity $i$ over path $p$.
The  all-or-nothing multi-commodity flow problem tries to find a maximum weight routable set:
\begin{equation}
\begin{aligned} \label{P}
&maximize  \sum_{i=1}^k w_i \times y_i\\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t. &\forall e \in E: \sum_{i=1}^k\sum_{p\in \mathcal{P}_i}f_{ip}L_{pe} \le c_e \\
     &\forall  1\le i \le k  : y_i=
\begin{cases}
1 &\text{$\sum_{p \in \mathcal{P}_i}f_{ip} \ge d_i$}\\
0 &\text{$\sum_{p\in \mathcal{P}_i}f_{ip} < d_i$}
\end{cases}\\
\end{array}
\end{aligned}
\end{equation}
Where $y_i$ denotes whether commodity flow $i$ is routable.
Consider a special case of the failure recovery problem, where $\mu_d=0$ for every $d$.
This means, if the allocated bandwidth is no less than the demand, 
then the profit is 1, or the profit is 0 otherwise.
We can transform the all-or-nothing multi-commodity flow problem to a special of our failure recovery problem by 
regarding the commodities as the BA demands.
%\textbf{TBD:
%We consider setting the admitted demand from tenants and their bandwidth target in 
%the failure recovery as the multi-commodities and their bandwidth demand in the all-or-nothing multi-commodity flow problem.}
%If we can solve the special case of the admission control problem with a polynomial time algorithm, we would obtain the routable multi-commodity flow set  in the all-or-nothing multi-commodity flow problem.  
Therefore, the failure recovery problem is at least as hard as the all-or-nothing multi-commodity flow
problem, which is known to be NP-hard. This completes the proof.
%If we regard $j \in J$ as a multi-commodity flow pair and the topology as the undirected graph.
%$g_j$ denotes whether multi-commodity flow $j$ is able to be routed.
%Then WAPM-S problem can be seen as a variant of all-or-nothing multi-commodity flow problem and it is NP-hardness.
\end{proof}
